Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material

### 2017-07-24 sm.tex
[sm] update email, include original mcwf paper

\begin{document}
\title{Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material}
\author{Yichao Yu}
\author{Nicholas R. Hutzler}
\altaffiliation{Present address: California Institute of Technology, Division of Physics, Mathematics, and Astronomy.  Pasadena, CA, 91125}
\author{Jessie T. Zhang}
\author{Lee R. Liu}
\author{Kang-Kuen Ni}
\email{ni@chemistry.harvard.edu}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts, 02138, USA}

@@

We use a computer simulation to study the importance of different effects
and guide the optimization of Raman sideband cooling.
The simulation uses the quantum jump (or Monte-Carlo wavefunction) method~\cite{Chretien2014}
to accurately calculate the evolution within each laser pulse where different energy eigenstates
are assumed to decohere immediately upon spontaneous emission and on pulse boundaries.
Such approximations are valid and greatly simplify the computation
at the cost of limiting the applicability of the simulation to processes that require stronger
coherence, such as Ramsey spectroscopy or rapid push-out of the atoms from the trap
(faster than a trap oscillation period).

>>>>

\begin{document}
\title{Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material}
\author{Yichao Yu}
\email{yichaoyu@g.harvard.edu}
\author{Nicholas R. Hutzler}
\altaffiliation{Present address: California Institute of Technology, Division of Physics, Mathematics, and Astronomy. Pasadena, CA, 91125}
\author{Jessie T. Zhang}
\author{Lee R. Liu}
\author{Kang-Kuen Ni}
\email{ni@chemistry.harvard.edu}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts, 02138, USA}

@@

We use a computer simulation to study the importance of different effects
and guide the optimization of Raman sideband cooling.
The simulation uses the quantum jump (or Monte-Carlo wavefunction) method~\cite{Dalibard1992,Chretien2014}
to accurately calculate the evolution within each laser pulse where different energy eigenstates
are assumed to decohere immediately upon spontaneous emission and on pulse boundaries.
Such approximations are valid and greatly simplify the computation
at the cost of limiting the applicability of the simulation to processes that require stronger
coherence, such as Ramsey spectroscopy or rapid push-out of the atoms from the trap
(faster than a trap oscillation period).
